---
title: "Data Fabric of My Life"
output: html_document
---

M. Samuel - January 19th 2019

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)
library(dplyr)
library(wordcloud)
library(tm)

myTextSize <- 20
```
<br>
<br>
* Mostly suppressing all code, but keeping just a bit for nerds like Nava, Steve, and you (?), to keep me honest

```{r}
pDat              <- read.csv("PartyData.csv",as.is=TRUE)
pDat[is.na(pDat)] <- 0
pDat              <- filter(pDat,Who != "Michael")

myPie <- function(dat,lab,myCol=c("cyan","red"),myAngle=110) { 
         pie(table(dat),label=lab,
         init.angle=myAngle,
         col = myCol,
         cex=1.5)
}
```

<br>

```{r echo=FALSE, message=FALSE}
ggplot(pDat, aes(x=When)) + geom_histogram(fill="orange",color="black") + 
  theme(text = element_text(size = myTextSize)) +
  labs(x = "What year did we meet")

```

<br>
<br>

```{r}
ggplot(pDat, aes(x= forcats::fct_rev(forcats::fct_infreq(Where) ))) + 
     geom_bar(fill="red",color="black") +
     coord_flip()+ 
     theme(text = element_text(size = myTextSize)) + 
     labs(x = "Where did we meet")
```


<br>
<br>

## Proportion of each single relationship dimension

* several dimensions have complex definitions, contact author for further discussion
```{r echo=FALSE}
attach(pDat)
par(mfrow=c(2,2),oma=c(0,0,0,0),mar=c(0,2,0,3))
myPie(Samuel,  c("Not","Samuel"))
myPie(Schulman,c("Not","Schulman"))
myPie(Bearson, c("Not","Bearson"))
myPie(Jewish,  c("Not/Unk","Jewish"),myCol=c("white","blue"),myAngle=230)
myPie(Health,  c("Not/Unk","Health"))
myPie(UCB,     c("Not/Unk","UCB"))
myPie(Larkey,  c("Not","Neighbors"))
myPie(Men,     c("No","MEN"))
myPie(Books,   c("No","Books"))
myPie(Travel,  c("No/Unk","Travel"))
myPie(Lover,   c("No, definitely not","Lover"))
par(mfrow=c(1,1))
```

<br>
<br>


### Connection Dimentioality Score = sum of individual scores
```{r echo=FALSE }
ggplot(pDat, aes(x=Total)) + geom_bar(fill="green",color="black") + ylim(0, 20) +
  theme(text = element_text(size = myTextSize)) +
  labs(x = "Connection Dimentionality Score") +
  scale_x_continuous(breaks=seq(0,9,1))
```

<br>


* #### why are there several '0's' on dimentionality score
* #### review of raw data indicated a missing dimension, "B Connection" = persons who I know, originally, primarily by a connection to a Bearson

```{r}
myPie(BearsonDegree, c("Not","B Connection"))
```

* #### Corrected data.  Still a few "0's", but hardly 0's to me--mostly partners of people I have met more recently...
* #### And who has Score = 8?  Jane!
* #### And who has Score = 9?  Leah and Louis! (score higher than Jane because of their Schulman and Bearson blood)

```{r echo=FALSE}
ggplot(pDat, aes(x=Total2)) + geom_bar(fill="green",color="black") +
  theme(text = element_text(size = myTextSize)) +
  labs(x = "(B Corrected) Connection Dimentionality Score") + ylim(0, 20) +
  scale_x_continuous(breaks=seq(0,9,1))
```


<br>
<br>

### Time to take a puff, and examine a violin plot with jittered data, exploring the relationship of when we met to where we met

```{r echo=FALSE}
ggplot(pDat, aes(x=as.factor(Where2), y=When)) + 
              geom_violin(fill="purple",draw_quantiles = c(0.25, 0.5, 0.75)) +  
              geom_jitter(shape=16, color="blue",size=3,position=position_jitter(0.2)) +  
              theme(text = element_text(size = 10)) +
              labs(x = "Where")
```


<br>

## Putting it all together; yes LOTS of amazing stuff! But is that really it, my whole life? 
```{r echo=FALSE, warning=FALSE}
xwords <- c(rep("Samuel",sum(Samuel)),
            rep("Schulman",sum(Schulman)),
            rep("Bearson",sum(Bearson)),
            rep("Health",sum(Health)),
            rep("Books",sum(Books)),
            rep("Travel",sum(Travel)),
            rep("Jewish",sum(Jewish)/2),
            rep("UCB",sum(UCB)),
            Where,
            rep("Men",sum(Men))
            )
  
wordcloud(xwords,colors=brewer.pal(8, "Dark2"))

```

## Hardley...LOTS more details, sweetness, and love, based on a few words I wrote about every single one of you, and then put together this way:


```{r echo=FALSE, warning=FALSE}
wordcloud(c(pDat$Words,pDat$Words,pDat$Who),
          min.freq=1,
          rot.per=.3,
          scale=c(4,.5),
          colors=brewer.pal(8, "Dark2")
          )

```


<br>
<br>

## And, FINALLY, to wrap it up, thank you all!

```{r echo=FALSE, warning=FALSE}

wordcloud(c("LEARN","LOVE","COMMUNITY","GRATEFUL"),colors=c("red"),rot.per=.4)
```



```{r echo=FALSE}

# p <- p + theme(axis.text = element_text(size = 15)) # changes axis labels
# p <- p + theme(axis.title = element_text(size = 25)) # change axis titles
# p <- p + theme(text = element_text(size = 10)) # this will change all text size


```
